How do changes in ex vary between countries?

### 2022-03-09 draft_paper.Rmd

#using flextable
myft <- flextable(stat_sig_table)
myft
myft <- theme_vanilla(myft)
myft
```

>>>>

#using flextable
myft <- flextable(stat_sig_table)
myft
myft <- theme_vanilla(myft)
myft
```
Next, let's look closer at France, Scotland, and E&Ws life expectancy at birth for males.
Jon: can we somehow include these 3 in the below to produce a graph? I tried adding into the first chunk but it does not run the later parts.

```{r}
example_df <- 
  hmd_ex_selected_countries_with_synth %>% 
      filter(x == 0) %>% 
      filter(sex == "male") %>% 
      filter(code == "FRATNP") %>% 
      filter(year >= 1979)

grid_search_df %>% 
  ggplot(aes(tau_candidate, aic)) + 
  geom_point()
```
